---
title: "Excercise 1 Boostrapping"
author: "Tiffany Sung"
date: "8/6/2018"
output: html_document
---

```{r}
library(mosaic)
library(quantmod)
library(foreach)
```

```{r}
# Import the five ETFs
mystocks = c("SPY", "TLT", "LQD", "EEM", "VNQ")
myprices = getSymbols(mystocks, from = "2007-01-01")
getSymbols(mystocks)

#Get the adjusted closing price of each ETF
for(ticker in mystocks) {

  expr = paste0(ticker, "a = adjustOHLC(", ticker, ")")
  eval(parse(text=expr))
}

# Combine all the returns in a matrix
all_returns = cbind(ClCl(LQDa),ClCl(TLTa),ClCl(SPYa), ClCl(VNQa), ClCl(EEMa))
all_returns = as.matrix(na.omit(all_returns))

head(all_returns)
```

```{r}
# Plot each versus the other for approximate correlation
pairs(all_returns)
# The sample correlation matrix
cor(all_returns)
```

From the mean and variance of each ETFs, we can see that EEM, VNQ have relatively higher return, but higher risk consequently.
Thus, we can then assume EEM and VNQ is a risker investment compare to the other ETFs.
```{r}
#The mean and variance
sort(apply(all_returns,2,mean),decreasing = TRUE)
cat("\n")
sort(apply(all_returns,2,var),decreasing = TRUE)
```

```{r}
par(mfrow=c(2,3))
hist(all_returns[SPYa], 30, xlim=c(-0.04, 0.04))
hist(all_returns[TLTa], 30, xlim=c(-0.04, 0.04))
hist(all_returns[LQDa], 30, xlim=c(-0.04, 0.04))
hist(all_returns[EEMa], 30, xlim=c(-0.04, 0.04))
hist(all_returns[VNQa], 30, xlim=c(-0.04, 0.04))
```


**Evenly Weighted Portfolio**
First, we construct a portfolio which the initial wealth is evenly distributed into each ETFs.
```{r}
initial_wealth = 100000
sim_even_split = foreach(i=1:5000, .combine='rbind') %do% {
  total_wealth = initial_wealth
  weights = c(0.2, 0.2, 0.2, 0.2, 0.2) #seperate evenly
  holdings = weights * total_wealth
  n_days = 20
  wealthtracker = rep(0, n_days)
  for(today in 1:n_days) {
    return.today = resample(all_returns, 1, orig.ids=FALSE)
    holdings = holdings + holdings*return.today #p+r(stock)
    total_wealth = sum(holdings)#p+r(portfolio)
    wealthtracker[today] = total_wealth
    holdings = total_wealth * weights #daily rebalance
  }
  wealthtracker
}
```

After we boostrap 
```{r}
even_mean <- mean(sim_even_split[,n_days])
even_return <- (mean(sim_even_split[,n_days])-initial_wealth)/initial_wealth
even_5_perc <- quantile(sim_even_split[,n_days], 0.05) - initial_wealth

# Print out results
cat("For an even split investment of $100,000,\nExpected holdings:", even_mean, "\nReturn Rate:", even_return, "\n5% VaR:", even_5_perc)
```

**Safer Portfolio**
Then, according to the mean and variance analysis of each ETFs, we want to construct a more risk-adverse portfolio by placing more holdings on SPY,TLT, LQD.
```{r}
# Now simulate many different possible scenarios when investing
# over a 4-week (20 trading day) period
initial_wealth = 100000
sim_safe_split = foreach(i=1:5000, .combine='rbind') %do% {
  total_wealth = initial_wealth
  weights = c(0.5, 0.3, 0.2, 0, 0) # 0.2 SPY, 0.3 TLT, 0.5 LQD
  holdings = weights * total_wealth
  n_days = 20
  wealthtracker = rep(0, n_days)
  for(today in 1:n_days) {
    return.today = resample(all_returns, 1, orig.ids=FALSE)
    holdings = holdings + holdings*return.today
    total_wealth = sum(holdings)
    wealthtracker[today] = total_wealth
    holdings = total_wealth * weights
  }
  wealthtracker
}
#safe_hist = hist(sim_safe_split[,n_days]- initial_wealth, breaks=30)
```

```{r}
safe_mean <- mean(sim_safe_split[,n_days])
safe_return <- (mean(sim_safe_split[,n_days])-initial_wealth)/initial_wealth
safe_5_perc <- quantile(sim_safe_split[,n_days], 0.05) - initial_wealth

# Print out results
cat("For an safer split investment of $100,000,\nExpected holdings:",safe_mean, "\nReturn Rate:", safe_return, "\n5% VaR:", safe_5_perc)
```

**Aggressive Portfolio**
For the aggressive portfolio, we merely place our initial wealth on the risker investment EEM and VNQ.
```{r}
initial_wealth = 100000
sim_risky_split = foreach(i=1:5000, .combine='rbind') %do% {
  total_wealth = initial_wealth
  weights = c(0, 0, 0, 0.3, 0.7) #0.7 EEM, 0.3 VNQ
  holdings = weights * total_wealth
  n_days = 20
  wealthtracker = rep(0, n_days)
  for(today in 1:n_days) {
    return.today = resample(all_returns, 1, orig.ids=FALSE)
    holdings = holdings + holdings*return.today
    total_wealth = sum(holdings)
    wealthtracker[today] = total_wealth
    holdings = total_wealth * weights
  }
  wealthtracker
}
#risk_hist = hist(sim_risky_split[,n_days]- initial_wealth, breaks=30)
```

```{r}
risky_mean <- mean(sim_risky_split[,n_days])
risky_return <- (mean(sim_risky_split[,n_days])-initial_wealth)/initial_wealth
risky_5_perc <- quantile(sim_risky_split[,n_days], 0.05) - initial_wealth

# Print out results
cat("For a risky split investment of $100,000,\nExpected holdings:", risky_mean, "\nReturn Rate:", risky_return, "\n5% VaR:", risky_5_perc)
```

```{r}
even = sim_even_split[,n_days]- initial_wealth
safe = sim_safe_split[,n_days]- initial_wealth
risk = sim_risky_split[,n_days]- initial_wealth

plot_df = data.frame(even, safe, risk)

ggplot(data = plot_df) + 
    geom_histogram(aes(risk),fill = 'red4',alpha = 0.9,position="stack")+
    geom_histogram(aes(even),fill = 'salmon1',alpha = 0.6,position="stack") + 
    geom_histogram(aes(safe),fill = 'olivedrab4',alpha = 0.3,position="stack")+
    scale_fill_brewer(palette="Spectral")+
    xlim(c(-25000,60000))+
    xlab('Portfolio Profit/Loss Spread')+
    ylab('Frequency')
```

**Evaluate Portfolio Performance**
```{r}
get_return = function(initial_wealth,weights,all_returns){
    
    sim_split = foreach(i = 1:5000, .combine = 'rbind') %do% {
        total_wealth = initial_wealth
        holdings = weights * total_wealth
        n_days = 20
        wealthtracker = rep(0, n_days)
        for(today in 1:n_days) {
            return.today = resample(all_returns, 1, orig.ids=FALSE)
            holdings = holdings + holdings*return.today #p+r(stock)
            total_wealth = sum(holdings)#p+r(portfolio)
            wealthtracker[today] = total_wealth
            holdings = total_wealth * weights #daily rebalance
        }
        wealthtracker
    }
    return(quantile(sim_split[,n_days], 0.05) - initial_wealth)
}  

#weight_even = rep(0.2,5)
#even = get_return(100000,weight_uni,all_returns)
```

```{r}
weight = runif(5)
weight = weight / sum(weight)
for (i in 1:3){
    weight = runif(5)
    weight = weight / sum(weight)
    initial_wealth = 100000
    VaR = get_return(initial_wealth,weight,all_returns)
    cat('The portfolio weight is: ')
    print(weight)
    cat('VaR of the portfolio is: ')
    print(VaR)
}
```

